Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-10-03 paper_comparison/paper_comparison/paper_comparison.Rmd
clean up results

### Assigning subjects

Three replications are made for each of the parameter values shown in Table \ref{tab:parameter-table} resulting in 443 different lineups. For each lineup, the actual data plot was drawn as a standard residual plot of the null model with raw residuals on the y-axis and fitted values on the x-axis. The 19 null datasets were generated by the residual rotation technique, and plotted in the same way. The lineup consisted of 20 residual plots with one randomly placed actual data plot.

In addition, each lineup is designed to be evaluated by five different subjects to provide reasonable estimates of the visual p-value.

Thus, $192 \times 3 \times 5 / (20 - 2) = 160$ subjects were recruited to satisfy the design of the experiment I.

@@

software/technical

## Power comparison

@@

```{r}
vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  rename(p_value_dirichlet = p_value_select_all_plots) %>%
  ggplot() +
  geom_point(aes(p_value_uniform, p_value_dirichlet)) +
  geom_abline() +
  scale_x_log10() +
  scale_y_log10()
```

@@

```{r}
vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(reject_uniform = as.numeric(p_value_uniform <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value_dirichlet"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value_dirichlet"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject_uniform, col = "VI_p_value_uniform"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_uniform, times = 500), 
              aes(log_effect_size, reject_uniform, group = boot_id, col = "VI_p_value_uniform"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  facet_wrap(~x_dist) +
  ggtitle("poly")
```

@@

```{r}
vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(reject_uniform = as.numeric(p_value_uniform <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value_dirichlet"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value_dirichlet"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject_uniform, col = "VI_p_value_uniform"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_uniform, times = 500), 
              aes(log_effect_size, reject_uniform, group = boot_id, col = "VI_p_value_uniform"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  facet_wrap(~x_dist) +
  ggtitle("heter")
```

```{r}
p_value_cache_env <- new.env()

if (file.exists(here::here("data/p_value_only_5_eval.rds"))) {
  p_value_only_5_eval <- readRDS(here::here("data/p_value_only_5_eval.rds"))
} else {
  p_value_only_5_eval <- vi_survey_processed %>%
  filter(x_dist == "uniform") %>%
  filter((is.na(b) & e_sigma != 0.125 ) | (b != 0 & b < 128)) %>%
  filter(exp != 5) %>%
  group_by(unique_lineup_id) %>%
  summarise(p_value_only_5_eval = calc_p_value(n_detect = sum(detect), 
                                               n_eval = n(), 
                                               n_sel = num_selection, 
                                               dist = "dirichlet",
                                               alpha = numeric_alpha[1],
                                               cache_env = p_value_cache_env))

  saveRDS(p_value_only_5_eval, here::here("data/p_value_only_5_eval.rds"))
}

vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(x_dist == "uniform") %>%
  filter(b != 0) %>%
  filter(b < 128) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  left_join(p_value_only_5_eval) %>%
  mutate(reject_only_5_eval = as.numeric(p_value_only_5_eval <= 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject_only_5_eval, col = "VI_p_value_only_5_eval"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_only_5_eval, times = 500), 
              aes(log_effect_size, reject_only_5_eval, group = boot_id, col = "VI_p_value_only_5_eval"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  ggtitle("heter")

p1 <- vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(x_dist == "uniform") %>%
  filter(b != 0) %>%
  filter(b < 128) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  left_join(p_value_only_5_eval) %>%
  mutate(reject_only_5_eval = as.numeric(p_value_only_5_eval <= 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03)

p2 <- vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(x_dist == "uniform") %>%
  filter(b != 0) %>%
  filter(b < 128) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  left_join(p_value_only_5_eval) %>%
  mutate(reject_only_5_eval = as.numeric(p_value_only_5_eval <= 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_only_5_eval, col = "VI_p_value_only_5_eval"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_only_5_eval, times = 500), 
              aes(log_effect_size, reject_only_5_eval, group = boot_id, col = "VI_p_value_only_5_eval"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03)

patchwork::wrap_plots(p1, p2)
```

vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(x_dist == "uniform") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  left_join(p_value_only_5_eval) %>%
  mutate(reject_only_5_eval = as.numeric(p_value_only_5_eval <= 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(aes(log_effect_size, reject_only_5_eval, col = "VI_p_value_only_5_eval"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_only_5_eval, times = 500), 
              aes(log_effect_size, reject_only_5_eval, group = boot_id, col = "VI_p_value_only_5_eval"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  ggtitle("poly")

p1 <- vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(x_dist == "uniform") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  left_join(p_value_only_5_eval) %>%
  mutate(reject_only_5_eval = as.numeric(p_value_only_5_eval <= 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03)

p2 <- vi_survey_processed %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(x_dist == "uniform") %>%
  filter(e_sigma != 0.125) %>%
  mutate(reject_dirichlet = as.numeric(p_value_select_all_plots <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  left_join(p_value_only_5_eval) %>%
  mutate(reject_only_5_eval = as.numeric(p_value_only_5_eval <= 0.05)) %>%
  ggplot() +
  geom_smooth(aes(log_effect_size, reject_only_5_eval, col = "VI_p_value_only_5_eval"), method = "glm", method.args = list(family = binomial), se = FALSE) +
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_only_5_eval, times = 500), 
              aes(log_effect_size, reject_only_5_eval, group = boot_id, col = "VI_p_value_only_5_eval"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03)

patchwork::wrap_plots(p1, p2)

```{r eval = FALSE}
vi_survey_processed %>%
  filter(exp == 3) %>%
  filter(e_sigma != 0.125) %>%
  mutate()

vi_survey_processed %>%
  filter(exp == 3) %>%
  filter(e_sigma != 0.125) %>%
  mutate(set = factor(set), lineup_id = factor(lineup_id)) %>%
  {lme4::glmer(weighted_detect ~ effect_size + ( 0 + effect_size | set) + ( 0 + effect_size | lineup_id), family = binomial ,data = .)} %>%
  predict(type = "response")

  ggplot() +
  geom_smooth(aes(log_effect_size, reject_dirichlet, col = "VI_p_value"), method = "glm", method.args = list(family = binomial), se = FALSE)

+
  stat_smooth(geom = "line", 
              data = ~boot_y(.x, reject_dirichlet, times = 500), 
              aes(log_effect_size, reject_dirichlet, group = boot_id, col = "VI_p_value"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE, 
              alpha = 0.03) +
  geom_smooth(data = mutate(poly_conv_sim, log_effect_size = log(effect_size)) %>%
                pivot_longer(F_p_value:SW_p_value), 
              aes(log_effect_size, as.numeric(value < 0.05), col = name), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  facet_wrap(~x_dist) +
  ggtitle("poly")

  ?glm
```

<!-- # Old stuff -->

<!-- ## Computing power curves -->

<!-- For the purpose of examining the effectiveness of visual test in regression diagnostics, two experiments were conducted. The experiment I has ideal scenario for conventional testing, where the visual test is not expected to outperform the conventional test. The experiment II is a scenario where the conventional test is an approximate test, in which the visual test may have a chance to match the performance of the conventional test. -->

<!-- Subjects for both experiments were recruited from an crowdsourcing platform called Prolific [ref here]. Prescreening procedure was applied during the recruitment, subjects were required to be fluent in English, with $98\%$ minimum approval rate in other studies and 10 minimum submissions. -->

<!-- During the experiment, every subject was presented with a block of 20 lineups. And for every lineup, the subject was asked to select one or more plots that are most different from others, provide a reason for their selections, and evaluate how different they think the selected plots were from others. If there was no noticeable difference between plots in a lineup, subjects were permitted to select zero plots without providing the reason. No subject was shown the same lineup twice. Information about preferred pronoun, age group, education, and previous experience in visual experiment were also collected. -->

<!-- A pool of 12 different lineups with obvious visual patterns were generated for experiment I and experiment II respectively. In every block of 20 lineups that presented to a subject, two out of 12 lineups were included as attention checks. A subject's submission was only accepted if the actual data plot was identified for at least one attention check. Data of rejected submissions were discarded automatically to maintain the overall data quality. -->

<!-- ## Non-linearity -->

<!-- Experiment I is designed to study the ability of human subjects to detect the effect of a random vector $\boldsymbol{z}$ which is a probabilist's Hermite polynomial [Herimite ref here] of another random vector $\boldsymbol{x}$ in a two variable statistical model formulated as: -->

<!-- ```{=tex} -->
<!-- \begin{align} \label{eq:nonlinearity-model} -->
<!-- \boldsymbol{y} = 1 + \boldsymbol{x} + \boldsymbol{z} + \boldsymbol{\varepsilon},\\ -->
<!-- \boldsymbol{x} = g(\boldsymbol{x}_{raw}, 1), \\ -->
<!-- \boldsymbol{z} = g(\boldsymbol{z}_{raw}, 1), \\ -->
<!-- \boldsymbol{z}_{raw} = He_j(g(\boldsymbol{z}, 2)), -->
<!-- \end{align} -->
<!-- ``` -->
<!-- where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$, $\boldsymbol{x}_{raw}$, $\boldsymbol{z}_{raw}$ are vector of size $n$, $He_{j}(.)$ is the $j$th-order probabilist's Hermite polynomials, $\varepsilon \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$, and $g(\boldsymbol{x}, k)$ is a scaling function to enforce the support of the random vector to be $\{-k, k\}$ defined as -->

<!-- ```{=tex} -->
<!-- \begin{equation} \label{eq:scaling-function} -->
<!-- g(\boldsymbol{x}, k) = (\boldsymbol{x} - min(\boldsymbol{x}))/max(\boldsymbol{x} - min(\boldsymbol{x})) \times 2k - k, \quad \text{for} \quad k > 0.  -->
<!-- \end{equation} -->
<!-- ``` -->
<!-- The null regression model used to fit the realizations generated by the above model is formulated as: -->

<!-- ```{=tex} -->
<!-- \begin{equation} \label{eq:scaling-function} -->
<!-- \boldsymbol{y} = \beta_0 + \beta_1 \boldsymbol{x} + \boldsymbol{u}, -->
<!-- \end{equation} -->
<!-- ``` -->
<!-- where $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$. -->

<!-- Model misspecification presents since the null model leaves out the higher order term. -->

<!-- Experiment data were simulated using four different order of probabilist's Hermite polynomials ($j = 2, 3, 6, 18$), three different sample sizes (n = 50, 100, 300) , four different standard deviations of the error ($\sigma$ = 0.5, 1, 2, 4) and four different distribution of $X_{raw}$: (1) $U(-1, 1)$, (2) $N(0, 0.3^2)$, (3) $lognormal(0, 0.6^2)/3$ and (4) $u\{1, 5\}$. A summary of the parameters used in this experiment is given in Table \ref{tab:parameter-table}. -->

<!-- The values of $j$ was chosen so that different shapes of non-linearity were included in the residual plot. These include "U" shape, "S" shape, "M" shape and "Triple-U" shape. -->

<!-- ```{r different-shape-of-herimite} -->
<!-- stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1 -->

<!-- ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300) -->

<!-- VI_MODEL$plot(ori_dat) +  -->
<!--   ggtitle(quote(He[2]:"U shape")) +  -->
<!--   theme_light() -> p1 -->

<!-- VI_MODEL$plot(poly_model(shape = 2, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300, computed = select(ori_dat, x, e))) + -->
<!--   ggtitle(quote(He[3]:"S shape")) +  -->
<!--   theme_light() -> p2 -->

<!-- VI_MODEL$plot(poly_model(shape = 3, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300, computed = select(ori_dat, x, e))) + -->
<!--   ggtitle(quote(He[6]:"M shape")) +  -->
<!--   theme_light() -> p3 -->

<!-- VI_MODEL$plot(poly_model(shape = 4, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300, computed = select(ori_dat, x, e))) + -->
<!--   ggtitle(quote(He[18]:"Triple-U shape")) +  -->
<!--   theme_light() -> p4 -->

<!-- patchwork::wrap_plots(p1, p2, p3, p4, ncol = 2) -->
<!-- ``` -->

<!-- The range of $\sigma$, which is a factor controlling the strength of the signal, was chosen so that different difficulty levels of lineups were generated, and therefore, the estimated power curve would be smooth and continuous. -->

<!-- ```{r different-sigma} -->
<!-- ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300) -->

<!-- VI_MODEL$plot(ori_dat) +  -->
<!--   ggtitle(quote(sigma~"="~0.5)) +  -->
<!--   theme_light() -> p1 -->

<!-- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 1)$gen(300, computed = select(ori_dat, x))) + -->
<!--   ggtitle(quote(sigma~"="~1)) +  -->
<!--   theme_light() -> p2 -->

<!-- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 2)$gen(300, computed = select(ori_dat, x))) + -->
<!--   ggtitle(quote(sigma~"="~2)) +  -->
<!--   theme_light() -> p3 -->

<!-- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 4)$gen(300, computed = select(ori_dat, x))) + -->
<!--   ggtitle(quote(sigma~"="~4)) +  -->
<!--   theme_light() -> p4 -->

<!-- patchwork::wrap_plots(p1, p2, p3, p4, ncol = 2) -->
<!-- ``` -->

<!-- Four different distribution were used to generate $X_{raw}$. The uniform and the normal distribution are symmetric and commonly assumed in statistical models. The adjusted log-normal distribution provides skewed density. And the discrete uniform distribution provides discreteness in residual plot, which could enrich the pool of visual patterns. -->

<!-- ```{r different-dist} -->
<!-- ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300) -->

<!-- VI_MODEL$plot(ori_dat) +  -->
<!--   ggtitle(quote(U(-1,1))) +  -->
<!--   theme_light() -> p1 -->

<!-- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300, computed = select(ori_dat, e))) + -->
<!--   ggtitle(quote(N(0,0.3^2))) +  -->
<!--   theme_light() -> p2 -->

<!-- VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))}, sigma = 0.5)$gen(300, computed = select(ori_dat, e))) + -->
<!--   ggtitle(quote(lognormal(0,0.6^2)/3)) +  -->
<!--   theme_light() -> p3 -->

<!-- VI_MODEL$plot(poly_model(shape = 1, x = rand_uniform_d(k = 5, even = TRUE), sigma = 0.5)$gen(300, computed = select(ori_dat, e))) + -->
<!--   ggtitle(quote(U~"{1,5}")) +  -->
<!--   theme_light() -> p4 -->

<!-- patchwork::wrap_plots(p1, p2, p3, p4, ncol = 2) -->
<!-- ``` -->

<!-- Three replications are made for each of the parameter values shown in Table \ref{tab:parameter-table} resulting in 192 different lineups. For each lineup, the actual data plot was drawn as a standard residual plot of the null model with raw residuals on the y-axis and fitted values on the x-axis. The 19 null datasets were generated by the residual rotation technique, and plotted in the same way. The lineup consisted of 20 residual plots with one randomly placed actual data plot. Figure \ref{fig:example-lineup} is an example of one of these lineups. It was produced by using $n = 300$, $j = 6$, $\sigma = 0.5$ and $X_{raw} \sim N(0.0.3^2)$. The actual data plot location was four. All five subjects correctly identified the actual data plot for this lineup. -->

<!-- ```{r example-lineup, fig.cap="Example lineup \\label{fig:example-lineup}"} -->
<!-- VI_MODEL$plot_lineup(polynomials_lineup[[23]]$data,  -->
<!--                      remove_grid_line = TRUE,  -->
<!--                      theme = theme_light(), -->
<!--                      remove_axis = TRUE) -->
<!-- ``` -->

<!-- <!-- It was generated for $n = 1$, $\sigma = 1$, $j = 1$, $X_{raw} \sim N$. For this lineup, x out of k observers picked the actual data plot. Each lineup is evaluated by 5 different subjects to provide reasonable estimates of the p-value. --> -->

<!-- In addition, each lineup is designed to be evaluated by five different subjects to provide reasonable estimates of the visual p-value. Thus, $192 \times 3 \times 5 / (20 - 2) = 160$ subjects were recruited to satisfy the design of the experiment I. -->

<!-- Experiment II is designed to study the ability of human subjects to detect the appearance of a heteroskedasticity pattern under a simple linear regression model setting: -->

<!-- ```{=tex} -->
<!-- \begin{align} \label{eq:heter-model} -->
<!-- \boldsymbol{y} = 1 + \boldsymbol{x} + \boldsymbol{\varepsilon},\\ -->
<!-- \boldsymbol{\varepsilon} \sim N(\boldsymbol{0}, 1 + 2 - |a| b (\boldsymbol{x} - a)^2 \boldsymbol{I}), \\ -->
<!-- \end{align} -->
<!-- ``` -->
<!-- where $\boldsymbol{y}$, $\boldsymbol{x}$, $\boldsymbol{\varepsilon}$ are vector of size $n$. -->

<!-- The null regression model used to fit the realizations generated by the above model is formulated exactly the same as the model used in the first experiment: -->

<!-- ```{=tex} -->
<!-- \begin{equation}  -->
<!-- \boldsymbol{y} = \beta_0 + \beta_1 \boldsymbol{x} + \boldsymbol{u}, -->
<!-- \end{equation} -->
<!-- ``` -->
<!-- where $\boldsymbol{u} \sim N(\boldsymbol{0}, \sigma^2\boldsymbol{I}_n)$. -->

<!-- Model misspecification presents since the assumption about the constant error variance is violated. -->

<!-- Experiment data were simulated using three different shapes ($a$ = -1, 0, 1), five different values of $b$ (b = 0.25, 1, 4, 16, 64), three different sample sizes (n = 50, 100, 300) and four different distribution of $X_{raw}$: (1) $U(-1, 1)$, (2) $N(0, 0.3^2)$, (3) $lognormal(0, 0.6^2)/3$ and (4) $u\{1, 5\}$. A summary of the parameters used in this experiment is given in Table \ref{tab:parameter-table}. -->

<!-- The values of $a$ was chosen so that different shapes of heteroskedasticity were included in the residual plot. These include triangle shape, butterfly shape and inverse triangle shape. -->

<!-- ```{r different-shape-of-heter} -->
<!-- stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1 -->

<!-- ori_dat <- heter_model(a = -1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 128)$gen(300) -->

<!-- VI_MODEL$plot(ori_dat) +  -->
<!--   ggtitle(quote("Triangle shape")) +  -->
<!--   theme_light() -> p1 -->

<!-- VI_MODEL$plot(heter_model(a = 0, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 128)$gen(300, computed = select(ori_dat, x, e))) + -->
<!--   ggtitle(quote("Butterfly shape")) +  -->
<!--   theme_light() -> p2 -->

<!-- VI_MODEL$plot(heter_model(a = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, b = 128)$gen(300, computed = select(ori_dat, x, e))) + -->
<!--   ggtitle(quote("Inverse triangle shape")) +  -->
<!--   theme_light() -> p3 -->

<!-- patchwork::wrap_plots(p1, p2, p3, ncol = 3) -->
<!-- ``` -->

<!-- The range of $b$, which is a factor controlling the strength of the signal, was chosen so that different difficulty levels of lineups were generated, and therefore, the estimated power curve would be smooth and continuous. -->

<!-- # Analysis and results -->

<!-- ## Data overview -->

@@

<!-- Subjects recruited from Prolific received a fixed payment for participating in the experiment. However, some subjects will try to maximize their earnings for minimum effort. During the review of submissions, if we found a subject objectively demonstrated clear low-effort throughout the experiment, i.e., failed all attention checks, we rejected the submission. The rejected submissions will be removed immediately, and Prolific will automatically recruit another subject as substitution. Therefore, we only paid for approved submissions and no further data screening procedure needed to be applied on the collected data. -->

<!-- A subject was allowed to select zero plots for a lineup if there was no visible difference between plots, but the simulated visual p-value given in Equation (\ref{eq:p-value-multi}) will effectively drop the subject from the simulation for this case, leading to inaccurate estimation of $p$-value. Therefore, we treated this case as making one selection but failing to identify the actual data plot so that Equation (\ref{eq:p-value-multi}) can be applied correctly. -->

<!-- In overall, there were a total of 3200 lineup evaluations made by 160 subjects in both experiment I and experiment II respectively, where 320 lineup evaluations were attention checks and were not used in the following analysis. -->

<!-- The collated dataset is provided in `polynomials` and `heter` of the `visage` `R` package. -->

<!-- ##  -->

>>>>

### Subject allocation

Three replications are made for each of the parameter values shown in Table \ref{tab:parameter-table} resulting in 1152 different lineups. In addition, each lineup is designed to be evaluated by five different subjects and lineups with uniform distribution is designed to be evaluated by 11 subjects to provide reasonable estimates of the visual p-value.

Thus, $443$ subjects were recruited to satisfy the design of the experiment. 
<!-- TODO:subject allocation algorithm -->

@@

<!-- TODO:pipeline description -->

## Results

### Power comparison

@@

@@

@@

### Data overview

@@

Subjects recruited from Prolific received a fixed payment for participating in the experiment. However, some subjects will try to maximize their earnings for minimum effort. During the review of submissions, if we found a subject objectively demonstrated clear low-effort throughout the experiment, i.e., failed all attention checks, we rejected the submission. The rejected submissions will be removed immediately, and Prolific will automatically recruit another subject as substitution. Therefore, we only paid for approved submissions and no further data screening procedure needed to be applied on the collected data.

In overall, there were a total of 3200 lineup evaluations made by 160 subjects in both experiment I and experiment II respectively, where 320 lineup evaluations were attention checks and were not used in the following analysis.

The collated dataset is provided in `vi_survey` of the `visage` `R` package.

### 2022-10-03 paper_comparison/paper_comparison/paper_comparison.tex
clean up results

\hypertarget{assigning-subjects}{%
\subsubsection{Assigning subjects}\label{assigning-subjects}}

Three replications are made for each of the parameter values shown in
Table \ref{tab:parameter-table} resulting in 443 different lineups. For
each lineup, the actual data plot was drawn as a standard residual plot
of the null model with raw residuals on the y-axis and fitted values on
the x-axis. The 19 null datasets were generated by the residual rotation
technique, and plotted in the same way. The lineup consisted of 20
residual plots with one randomly placed actual data plot.

Overall, we planned to collect 7974 evaluations on 1152 uniqued lineups
performed by 443 subjects throughout three experiment.

In addition, each lineup is designed to be evaluated by five different
subjects to provide reasonable estimates of the visual p-value.

Thus, \(192 \times 3 \times 5 / (20 - 2) = 160\) subjects were recruited
to satisfy the design of the experiment I.

@@

software/technical

\hypertarget{power-comparison}{%
\subsection{Power comparison}\label{power-comparison}}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-8-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-9-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-10-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-11-1}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-11-2}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-12-1}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-12-2}

>>>>

\hypertarget{subject-allocation}{%
\subsubsection{Subject allocation}\label{subject-allocation}}

Three replications are made for each of the parameter values shown in
Table \ref{tab:parameter-table} resulting in 1152 different lineups. In
addition, each lineup is designed to be evaluated by five different
subjects and lineups with uniform distribution is designed to be
evaluated by 11 subjects to provide reasonable estimates of the visual
p-value.

Thus, \(443\) subjects were recruited to satisfy the design of the
experiment.

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

\hypertarget{power-comparison}{%
\subsubsection{Power comparison}\label{power-comparison}}

@@

\hypertarget{data-overview}{%
\subsubsection{Data overview}\label{data-overview}}

Subjects recruited from Prolific received a fixed payment for
participating in the experiment. However, some subjects will try to
maximize their earnings for minimum effort. During the review of
submissions, if we found a subject objectively demonstrated clear
low-effort throughout the experiment, i.e., failed all attention checks,
we rejected the submission. The rejected submissions will be removed
immediately, and Prolific will automatically recruit another subject as
substitution. Therefore, we only paid for approved submissions and no
further data screening procedure needed to be applied on the collected
data.

In overall, there were a total of 3200 lineup evaluations made by 160
subjects in both experiment I and experiment II respectively, where 320
lineup evaluations were attention checks and were not used in the
following analysis.

The collated dataset is provided in \texttt{vi\_survey} of the
\texttt{visage} \texttt{R} package.
